\chapter{Conclusion and Future Work}
%\clearpage
%\section{Conclusion and Future Scope}
%\label{sec: Conclusion}
In the present work, a new framework to design the time-frequency localization optimized two-channel wavelet filter banks has been devised. In the devised framework, the prescribed number of vanishing moments ($V < \frac{L}{2}$) can be achieved. We formulated a non-convex problem into a convex problem using trace parameterization of the quadratic forms. Three design problems have been proposed to design the time-frequency optimized filter banks. We discussed 8 design examples from all the three design problems, with different input parameters to investigate the role and effectiveness of each parameter and the design methodology. 

The three design problems proposed in the present work are convex in matrix $\mathbf{X}$, from which we compute the autocorrelation function followed by the computation of analysis low-pass filter coefficients using the spectral factorization, which may or may not give the optimal filter. Approaches to find the optimal filter from the optimal matrix $\mathbf{X^{opt}}$ can be further investigated and devised.

The trade-offs among the different input parameters to the proposed design problems can be further investigated.
The effect of time-frequency localization on the frequency response parameters like roll-off factor, pass-band ripples can be further extended.

In the proposed work, the objective function was taken to be CCTFV, time variance and/ or the frequency variance of the analysis low-pass filter. The time-frequency measures for corresponding analysis wavelets can also be taken as the design optimality criterion to design the filter banks. 

Kha \cite{Kha} et al. designed symmetric orthogonal complex valued filter banks, the proposed orthogonal design can be extended to the design of complex valued orthogonal filter banks.
